---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load necessary libraries
```{r, message = FALSE}
# Load necessary libraries
# install.packages("classdata")
library(classdata)
library(ggplot2)

# Load the residential sales data
data(ames)

# Display the structure of the dataset
str(ames)

# Display the first few rows of the dataset
head(ames)

# Summary statistics of numerical variables
summary(ames)
```




# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.
